Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-01-29 paper/current/main.tex
resolving copyedits comment from reviwer #3

We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with a scaling parameter $r$, acting like a \textit{zooming lens}.
If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
Fig. \ref{fig:clustering}b demonstrates that regional relationships play a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
This suggests that the embedding space captures the hierarchical structure of mobility.

>>>>

We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a \textit{zooming lens}.
If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
Fig. \ref{fig:clustering}b demonstrates that regional relationships play a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
This suggests that the embedding space captures the hierarchical structure of mobility.
